A non-additive generalization of probability theory\\for quantum mechanics and beyond

### 2025-07-07 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex

@@

>>>>

%[This section has to make clear in what extra conditions on ensemble spaces Choquet theory can be applied.]

@@

A probability measure $\mu: \Omega_X \to \mathbb{R}$ over a sample space $X$ with $\sigma$-algebra $\Omega_X$ satisfies the three axioms by Kolmogorov
\begin{enumerate}[label={\Roman*}]
	\item\label{ax:pos} \textbf{Non-negativity:\,} $\forall x \in \Omega_X: \mu(x) \ge 0$
	\item\label{ax:norm} \textbf{Normalization:\,} $\mu(X) = 1$
	\item\label{ax:add} \textbf{$\sigma$-additivity:\,} $\mu ( \bigcup_i x_i ) = \sum_i \mu ( x_i )$ for any countable sequence of disjoint sets $x_i \in \Omega_X$.
\end{enumerate}
The last axiom is based on the (sometimes hidden) assumption of
\begin{enumerate}[label={\Roman*}]\setcounter{enumi}{3}
	\item\label{ax:exc} \textbf{Mutual exclusivity:\,} disjoint sets describe mutually exclusive events.
\end{enumerate}
